% !TeX program = xelatex
\documentclass{UAmathtalk}

\author{Susan Niefield}
\address{Union College}
\urladdr{http://www.math.union.edu/~niefiels/}
\title{Exactness and Projectivity}
\date{Thursday, April 30, 2015}

\usepackage{amsfonts}

\begin{document}

\maketitle

\begin{abstract}
We consider generalizations to monoidal categories of the tensor-hom relationship for modules over a commutative ring $R$, i.e., $-\otimes_R M$ is left adjoint to $\mathrm{Hom}_R(M,-)$ as endofunctors of $R$-Mod. For an object $V$ of a symmetric monoidal category $(\mathcal{V},\otimes,I,\dots)$, one can ask whether the endofunctor $-\otimes V$ has a right adjoint. If this is the case, for all $V$, then $\mathcal{V}$ is called a symmetric monoidal \emph{closed} category. There are many examples of symmetric monoidal closed categories. The existence of left adjoints to $-\otimes V$ is less common in many familiar monoidal categories. We say $V$ is \emph{exact} when such an adjoint exists.
For example, in the case of $R$-Mod, one can show that $M$ is exact if and only if $M$ is finitely generated and projective. The exact commutative $R$-algebras are precisely those which are exact when considered as $R$-modules. Our interest in the latter goes back to the late 1970s when we  were considering  the dual problem for the category of affine schemes over $\mathrm{Spec}R$. 

In this talk, we present a generalization of the above characterization of exact $R$-algebras which applies to several other categories. 
\end{abstract}

\end{document}
